This appendix presents a summary of each of the six team members' respective
contributions to this project.


\section*{Bas}
\begin{itemize}
    \item Prelimenary Kinect API testing.
    \item Point cloud viewer.
    \item OpenCV code bug fixing.
    \item Depth image to cube back projection system.
\end{itemize}

\section*{Jeroen}
\begin{enumerate}
\item eerste presentatie;
\item gewerkt aan vinden depth mapping algoritme
\end{enumerate}

\section*{Jimi}
\begin{itemize}
% Ik kan hier nog heel veel bijzetten aan tijdelijke testbestanden en zooi die ik gedaan heb, maar dat lijkt me niet echt nuttig
\item Modified Python wrappers for Freenect
\item Stereo calibration:
    \begin{itemize}
        \item theory
        \item implementation in \verb|stereo_calibrate_auto.py|
        \item tests
        \item report
    \end{itemize}
\item Alignment of images:
    \begin{itemize}
        \item theory
        \item implementation in \verb|rectify.py|
        \item tests
        \item report
    \end{itemize}
\item Getting `real' depth:
    \begin{itemize}
        \item found a good approximation
        \item implementation in \verb|rectify.py|
        \item report
    \end{itemize}
\end{itemize}

\section*{Joris}
\begin{itemize}
    \item project coordination;
    \item technical description of the Kinect (with Jeroen):
    \begin{itemize}
        \item collated and interpreted patents;
        \item collated and interpreted scholarly articles;
        \item prepared preliminary presentation;
        \item wrote technical description section of report;
    \end{itemize}
    \item edited Application section of report;
\end{itemize}

\section*{Lucas}
\begin{itemize}
\item Made up the algorithm we are using.
\item Created "create\_module.py" to implement the algorithm.
\item Created "calibrate.py" to make a calibrating framework and to do a 
straighforward single camera calibration. This was needed to better understand 
all matrices needed and to continue work on "create\_module.py".
\item Created undistort\_static.py to see the effect of the we found on some images.
\item Saved npy images so that we can work using static images (without the Kinect).
\item Created Kinect.py to combine everything.
\item Created npy\_to\_png.png to transform npy arrays to images we can open 
using a image viewer.
\item Wrote the subsections Creating a model and Combining it all in the 
application section of the report.
\item Author of the interim report.
\end{itemize}

\section*{Sander}
\begin{itemize}
    \item libfreenect and openkinect experimentation.
    \item Point cloud viewer.
    \item Depth image to cube back projection system.
\end{itemize}
